An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-09-13 paper/main.tex
fix an error
change on schedule & points to discuss

Points to discuss
\begin{itemize}
\item Schedule:
\item Introduction (story), Contribution, positions, examples, beginning of September?
\item zero draft : mid of September

\item When will be the deadline of PEPM2020 (October 18th)
\item ESOP (?)
\item Need to change the style file of latex..
\item []

\item Related work?
\item

\item TODO: %relationship between result (original vs \{cpg, kpg, xpg\})
%\item right assoc \& Recursive example?
%\item current foldr is not efficient? Are there any efficient foldr? Question to Prof. Hu.
%\item Language to show semantics: fi?, $f^{-1}$, $cond_{sv}$ and $cond_{s}$
%\item A good simple example of bx: Used in explanation of BiGUL and evaluation of pg.
%\item Related work: suggest?
%\item another pg ?? should be compared?
\end{itemize}

@@

The rest of this paper is the following. We introduce a subset of BiGUL, miniBiGUL, and show syntax, semantics, and properties in Section 2. Combining the semantics of put and get in Section 2, we construct $pg$ and show that it is self-inverse in Section 3.
We apply three optimizations to $pg$ in sequence. The first one is keeping update of BX lazily, and obtain $cpg$ in Section 4. The second one is lazy evaluation to avoid redundant computation, and obtain $kpg$ in Section 5. The third one is combination of $pg$ and $kpg$ in Section 6, because they are strong for different type of programs. In Section 7, we show experiemntal result of $pg$, $cpg$, $kpg$, $xpg$ and the original miniBiGUL.
In Section 8 we discuss about related work, and conclude in Section 9.

@@

\end{itemize}

\subsection{Construction of this paper}

\begin{itemize}
\item BiGUL 
\item pg (pair of put and get)
\item cpg (extention of pg. Keep eval information for reusing)
\item kpg (extention of cpg. Lazy evaluation)
\item xpg (combination of pg and kpg)
\item Experiment
\item Related work
\item Conclusion and Future work
\end{itemize}

@@

>>>>

Schedule
\begin{itemize}

\item Introduction (story), Contribution, positions, examples, beginning of September?
\item zero draft : mid of September

\item deadline of PEPM2020 (October 18th)
\item ESOP (?)
\item Need to change the style file of latex..
\item []
\end{itemize}

Points to discuss
\begin{itemize}
\item Introduction (story)
\item Contributions
\item Related work?
\item One week to revise current version.
  After that, Prof. Hu and Robert, could you send comments?

%\item TODO: %relationship between result (original vs \{cpg, kpg, xpg\})
%\item right assoc \& Recursive example?
%\item current foldr is not efficient? Are there any efficient foldr? Question to Prof. Hu.
%\item Language to show semantics: fi?, $f^{-1}$, $cond_{sv}$ and $cond_{s}$
%\item A good simple example of bx: Used in explanation of BiGUL and evaluation of pg.
%\item Related work: suggest?
%\item another pg ?? should be compared?
\end{itemize}

@@

The rest of this paper is the following. We introduce a subset of BiGUL, miniBiGUL, and show its syntax, semantics, and properties in Section 2. Combining the semantics of put and get in Section 2, we construct $pg$ and show that it is self-inverse in Section 3.
We apply three optimizations to $pg$ in sequence. The first one is keeping update of BX lazily, and we obtain $cpg$ in Section 4. The second one is lazy evaluation to avoid redundant computations, and we obtain $kpg$ in Section 5. The third one is combination of $pg$ and $kpg$ in Section 6, because they are strong for different type of programs. In Section 7, we show experiemntal results of $pg$, $cpg$, $kpg$, $xpg$ and miniBiGUL.
In Section 8 we discuss about related work, and conclude in Section 9.

@@

%\subsection{Construction of this paper}

%\begin{itemize}
%\item BiGUL 
%\item pg (pair of put and get)
%\item cpg (extention of pg. Keep eval information for reusing)
%\item kpg (extention of cpg. Lazy evaluation)
%\item xpg (combination of pg and kpg)
%\item Experiment
%\item Related work
%\item Conclusion and Future work
%\end{itemize}

@@

\begin{itemize}
\item BiGUL papers (PEPM, POPL, tutorial?)
\item the first BX paper
\item view update problem paper
\item get-based 
\end{itemize}
